---
title: "Tidymodels, Virtually"
author:
- name: Alison Hill, Ph.D.
  url: https://alison.rbind.io
  affiliation: RStudio
  affiliation_url: https://rstudio.com
date: "`r Sys.Date()`"
description: |
  An Introduction to Machine Learning with Tidymodels
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r meta, echo=FALSE}
library(metathis)
meta() %>%
  meta_general(
    description = "Tidymodels, Virtually",
    generator = "xaringan and remark.js"
  ) %>% 
  meta_name("github-repo" = "rstudio-education/tidymodels-virtually") %>% 
  meta_social(
    title = "Tidymodels, Virtually",
    url = "https://rstd.io/tip",
    image = "https://repository-images.githubusercontent.com/288797104/d13f1700-e2cc-11ea-9ed7-0bf3a41af1e4",
    image_alt = "",
    og_type = "website",
    twitter_card_type = "summary_large_image"
  )
```

## Welcome  

Thank you for enrolling in our workshop! These are the materials for an introductory machine learning workshop with tidymodels by Dr. Alison Presmanes Hill.

```{r, include=FALSE, fig.cap="[Slides](slides/index.html)"}
knitr::include_url("slides/index.html")
```


This four-hour workshop will provide a gentle introduction to machine learning with R using the modern suite of predictive modeling packages called [tidymodels](https://tidymodels.org). We will build, evaluate, compare, and tune predictive models. Along the way, we’ll learn about key concepts in machine learning including overfitting, the holdout method, the bias-variance trade-off, ensembling, cross-validation, and feature engineering. Learners will gain knowledge about good predictive modeling practices, as well as hands-on experience using tidymodels packages like [parsnip](https://tidymodels.github.io/parsnip), [rsample](https://tidymodels.github.io/rsample), [recipes](https://tidymodels.github.io/recipes/), [yardstick](https://tidymodels.github.io/yardstick/), [tune](https://tidymodels.github.io/tune/), and [workflows](https://tidymodels.github.io/workflows/).

\

## Prework

Please tune into class with a laptop that has the following installed:


<aside>
On the day of the class, we'll provide you with an RStudio Cloud project that contains all of the course materials. 
</aside>

* A recent version of R (>=3.9.0), which is available for free at <https://cran.r-project.org/>

* A recent version of RStudio Desktop (>=1.3.0), available for free at <https://www.rstudio.com/download> (RStudio Desktop Open Source License)

* The R packages we will use, which you can install by connecting to the internet, opening RStudio, and running at the command line:

    ```{r echo=TRUE, eval = FALSE}
    install.packages(c("tidyverse", "tidymodels", 
                       "remotes", "rpart.plot", "rattle", 
                       "vip", "AmesHousing", "kknn", 
                       "rpart", "ranger", "partykit"))
    
    # and
    
    remotes::install_github("tidymodels/modeldata")
    ```

<aside>
We will use the software listed above only as an important backup should there be problems with the classroom server connection.
</aside>

I look forward to meeting you,

Alison






\

## Links



+ [Slides](TBD)

## Workshops

Upcoming and past offerings:

- [R / Medicine 2020 Virtual Conference](https://events.linuxfoundation.org/r-medicine/)
- Becton, Dickinson and Company, Online
- Children's Hospital of Philadelphia, Online
- [rstudio::conf 2020](https://conf20-intro-ml.netlify.app/), San Francisco, CA, January 27 & 28 Training Days


## Acknowledgments {.appendix}

This is a website made with the [distill package](https://rstudio.github.io/distill/) and a custom theme by Alison Hill & [Desirée De Leon](https://desiree.rbind.io/).

