---
title: "02-workflows"
output: html_document
---

```{r setup, include=FALSE}
options(scipen = 999)
library(tidyverse)
library(modeldata)
library(tidymodels)

data("ad_data")
alz <- ad_data

# data splitting
set.seed(100) # Important!
alz_split  <- initial_split(alz, strata = Class, prop = .9)
alz_train  <- training(alz_split)
alz_test   <- testing(alz_split)

# data resampling
set.seed(100)
alz_folds <- 
    vfold_cv(alz_train, v = 10, strata = Class)

print("Welcome back, R/Medicine 2020!")
```

# Your Turn 1

workflow with formula

```{r}
tree_mod <- 
  decision_tree() %>% 
  set_engine(engine = "rpart") %>% 
  set_mode("classification")

tree_wf <-
  _____ %>% 
  add______(Class ~ .) %>% 
  add______(tree_mod)

tree_wf
```

```{r}
tree_mod <- 
  decision_tree() %>% 
  set_engine(engine = "rpart") %>% 
  set_mode("classification")

tree_wf <-
  workflow() %>% 
  add_formula(Class ~ .) %>% 
  add_model(tree_mod)

tree_wf
```


# Your Turn 2

Edit to fit the workflow instead.

```{r}
set.seed(100)
tree_mod %>% 
  fit_resamples(Class ~ ., 
                resamples = alz_folds) %>% 
  collect_metrics()
```

```{r}
set.seed(100)
tree_wf %>% 
  fit_resamples(resamples = alz_folds) %>% 
  collect_metrics()
```

# Your Turn 3

Write a recipe for predicting Class. 

Save the result as `alz_rec`  

```{r}
alz_rec <- 
  recipe(Class ~ ., data = alz) %>%
    step_other(Genotype, threshold = .05) %>%
    themis::step_downsample(Class, under_ratio = 2, seed = 100) 
```


# Your Turn 4

Make a workflow and fit it again.

```{r}
alzrec_wf <-
  workflow() %>% 
    add_recipe(alz_rec) %>% 
    add_model(tree_mod)

alzrec_wf %>% 
  fit_resamples(resamples = alz_folds) %>% 
  collect_metrics() 
```

# Your Turn 5

Create a new classification tree model spec; call it `big_tree_mod`. 
Set the cost complexity to `0`, and the minimum number of data points in a node to split to be `1`. 

Compare the metrics of the big tree to your previous results- which one predicts the test set better?

*Hint: you'll need https://parsnip.tidymodels.org/reference/decision_tree.html*


```{r}
big_tree_mod <-
  decision_tree(min_n = 1, cost_complexity = 0) %>% 
  set_engine("rpart") %>% 
  set_mode("classification")

big_tree_wf <- 
  alzrec_wf %>% 
  update_model(big_tree_mod)

set.seed(100)
big_tree_wf %>% 
  fit_resamples(resamples = alz_folds) %>% 
  collect_metrics()
```
