---
title: "03-tune"
output: html_document
---

```{r setup, include=FALSE}
options(scipen = 999)
library(tidyverse)
library(modeldata)
library(tidymodels)

data("ad_data")
alz <- ad_data

# data splitting
set.seed(100) # Important!
alz_split  <- initial_split(alz, strata = Class, prop = .9)
alz_train  <- training(alz_split)
alz_test   <- testing(alz_split)

# data resampling
set.seed(100)
alz_folds <- 
    vfold_cv(alz_train, v = 10, strata = Class)

print("Hey there, R/Medicine 2020 all-star!")
```

# Your Turn 1

Fill in the blanks to return the accuracy and ROC AUC for this model using 10-fold cross-validation.

```{r}
tree_mod <- 
  decision_tree() %>% 
  set_engine(engine = "rpart") %>% 
  set_mode("classification")

tree_wf <-
  workflows() %>% 
  add_formula(Class ~ .) %>% 
  add_model(tree_mod)

set.seed(100)
______ %>% 
  ______(resamples = alz_folds) %>% 
  ______
```

# Your Turn 2

Create a new parsnip model called `rf_mod`, which will learn an ensemble of classification trees from our training data using the **ranger** package. Update your `tree_wf` with this new model.

Fit your workflow with 10-fold cross-validation and compare the ROC AUC of the random forest to your single decision tree model --- which predicts the test set better?

*Hint: you'll need https://www.tidymodels.org/find/parsnip/*

```{r}
# model
rf_mod <-
  _____ %>% 
  _____("ranger") %>% 
  _____("classification")

# workflow
rf_wf <-
  tree_wf %>% 
  update_model(_____)

# fit with cross-validation
set.seed(100)
_____ %>% 
  fit_resamples(resamples = alz_folds) %>% 
  collect_metrics()
```


# Your Turn 3

Challenge: Fit 3 more random forest models, each using 3, 8, and 30 variables at each split. Update your `rf_wf` with each new model. Which value maximizes the area under the ROC curve?

```{r}
rf3_mod <- rf_mod %>% 
  set_args(mtry = 3) 

rf8_mod <- rf_mod %>% 
  set_args(mtry = 8) 

rf30_mod <- rf_mod %>% 
  set_args(mtry = 30) 
```

Do this for each model above:
```{r}
_____ <- rf_wf %>% 
  update_model(_____)

set.seed(100)
_____ %>% 
  fit_resamples(resamples = alz_folds) %>% 
  collect_metrics()
```


# Your Turn 4

Edit the random forest model to tune the `mtry` and `min_n` hyper-parameters; call the new model spec `rf_tuner`.

Update your workflow to use the tuned model.

Then use `tune_grid()` to find the best combination of hyper-parameters to maximize `roc_auc`; let tune set up the grid for you.

How does it compare to the average ROC AUC across folds from `fit_resamples()`?

```{r}
rf_mod <-
  rand_forest() %>% 
  set_engine("ranger") %>% 
  set_mode("classification")

rf_wf <-
  workflow() %>% 
  add_formula(Class ~ .) %>% 
  add_model(rf_mod)

set.seed(100) # Important!
rf_results <-
  rf_wf %>% 
  fit_resamples(resamples = alz_folds,
                metrics = metric_set(roc_auc),
                # change me to control_grid(verbose = TRUE) with tune_grid
                control = control_resamples(verbose = TRUE))

rf_results %>% 
  collect_metrics()
```


# Your Turn 5

Use `select_best()`, `finalize_workflow()`, and `last_fit()` to take the best combination of hyper-parameters from `rf_results` and use them to predict the test set.

How does our actual test ROC AUC compare to our cross-validated estimate?

```{r results='hide'}
alz_best <-
  rf_results %>% 
  _____(metric = "roc_auc")

last_rf_workflow <- 
  rf_wf%>%
  _____(alz_best) 

last_rf_fit <-
  last_rf_workflow %>% 
  _____(split = alz_split)

last_rf_fit %>% 
  collect_metrics()
```
