---
title: "03-recipes"
output: html_document
---

```{r setup, include=FALSE}
options(scipen = 999)
library(tidyverse)
library(AmesHousing)
library(tidymodels)

ames <- make_ames() %>% 
  dplyr::select(-matches("Qu"))

set.seed(100)
ames_split <- initial_split(ames)
ames_train <- training(ames_split)
ames_test  <- testing(ames_split)

rt_spec <- 
  decision_tree() %>% 
  set_engine("rpart") %>% 
  set_mode("regression")

# pca_rec <- 
#   recipe(Sale_Price ~ ., data = ames) %>%
#     step_novel(all_nominal()) %>%
#     step_dummy(all_nominal()) %>%
#     step_zv(all_predictors()) %>%
#     step_normalize(all_predictors()) %>%
#     step_pca(all_predictors(), num_comp = 5)
```

# Your Turn 1

Write a recipe for the `Sale_Price ~ `. variables that:
1. Adds a novel level to all factors  
2. Convert all factors to dummy variables  
3. Catches any zero variance variables  
4. Normalizes all of the predictors (centers and scales)
5. Computes the first 5 principal components  

Save the result as `pca_rec`  

```{r}
pca_rec <- 
  recipe(Sale_Price ~ ., data = ames) %>%
    step_novel(all_nominal()) %>%
    step_dummy(all_nominal()) %>%
    step_zv(all_predictors()) %>%
    step_normalize(all_predictors()) %>%
    step_pca(all_predictors(), num_comp = 5)
```


# Your Turn 2

Make a workflow that combines `pca_rec` and with `rt_spec`.

```{r}
pca_wf <-
  workflow() %>% 
    add_recipe(pca_rec) %>% 
    add_model(rt_spec)
```

# Your Turn 3

Try our pca workflow to predict sale price with the ames_test data. What is the RMSE?

```{r}
_______ %>% 
  fit(data = ames_train) %>% 
  predict(ames_test) %>% 
  mutate(truth = ames_test$Sale_Price) %>% 
  rmse(truth, .pred)
```

# Your Turn 4

Run the first chunk. Then try our pca workflow on `ames_folds`. What is the RMSE?

```{r}
set.seed(100)
ames_folds <- vfold_cv(ames_train, strata = Sale_Price, breaks = 4)
```

```{r}
pca_wf %>% 
  fit_resamples(resamples = ames_folds) %>% 
  collect_metrics()
```

# Your Turn 5

Modify the code below to build a new pca recipe that uses `step_other` *first* to collapse infrequently occurring values of `Neighborhood` into an "other" category. Then update `pca_wf` to use the new recipe.


```{r eval = FALSE}
other_rec <- 
  recipe(Sale_Price ~ ., data = ames) %>%
    step_novel(all_nominal()) %>%
    step_dummy(all_nominal()) %>%
    step_zv(all_predictors()) %>%
    step_normalize(all_predictors()) %>%
    step_pca(all_predictors(), num_comp = 5)

other_wf  <- 
  pca_wf %>% 
    ____________

_______ %>% 
  fit_resamples(resamples = _______) %>% 
  collect_metrics()
```

```{r}
other_rec <- 
  recipe(Sale_Price ~ ., data = ames) %>% 
    step_other(Neighborhood, threshold = 0.05) %>% 
    step_novel(all_nominal()) %>%
    step_dummy(all_nominal()) %>%
    step_zv(all_predictors()) %>%
    step_center(all_predictors()) %>%
    step_scale(all_predictors()) %>%
    step_pca(all_predictors(), num_comp = 5) 

other_wf <- 
  pca_wf %>% 
    update_recipe(other_rec)

other_wf %>% 
  fit_resamples(resamples = ames_folds) %>% 
  collect_metrics()
```

