---
title: "02-workflows"
output: html_document
---

```{r setup, include=FALSE}
options(scipen = 999)
library(tidyverse)
library(modeldata)
library(tidymodels)

data("ad_data")
alz <- ad_data

# data splitting
set.seed(100) # Important!
alz_split  <- initial_split(alz, strata = Class, prop = .9)
alz_train  <- training(alz_split)
alz_test   <- testing(alz_split)

# data resampling
set.seed(100)
alz_folds <- 
    vfold_cv(alz_train, v = 10, strata = Class)

# KNN model
knn_mod <-
  nearest_neighbor() %>%              
  set_engine("kknn") %>%             
  set_mode("classification") 

print("Welcome back, R/Medicine 2020!")
```

# Your Turn 1

Unscramble! You have all the steps from our `knn_rec`- your challenge is to *unscramble* them into the right order! 

Save the result as `knn_rec`

```{r}
step_dummy(all_nominal(), -all_outcomes())

step_normalize(all_numeric()) 

recipe(Class ~ ., data = alz)

step_novel(all_nominal(), -all_outcomes()) 

step_zv(all_predictors()) 

step_other(Genotype, threshold = .03) 
```

Answer:
```{r}
knn_rec <- 
  recipe(Class ~ ., data = alz) %>%
  step_other(Genotype, threshold = .03) %>% 
  step_novel(all_nominal(), -all_outcomes()) %>% 
  step_dummy(all_nominal(), -all_outcomes()) %>% 
  step_zv(all_predictors()) %>% 
  step_normalize(all_numeric()) 
```

# Your Turn 2

Fill in the blanks to make a workflow that combines `knn_rec` and with `knn_mod`.

```{r}
knn_wf <-
  ______ %>% 
  ______(knn_rec) %>% 
  ______(knn_mod)
knn_wf
```

```{r}
knn_wf <-
  workflow() %>% 
  add_recipe(knn_rec) %>% 
  add_model(knn_mod)
knn_wf
```

# Your Turn 3

Edit the code chunk below to fit the entire `knn_wflow` instead of just `knn_mod`.

```{r}
set.seed(100)
knn_mod %>% 
  fit_resamples(Class ~ ., 
                resamples = alz_folds) %>% 
  collect_metrics()
```

Answer:
```{r}
set.seed(100)
knn_wf %>% 
  fit_resamples(resamples = alz_folds) %>% 
  collect_metrics()
```

# Your Turn 4

Turns out, the same `knn_rec` recipe can also be used to fit a penalized logistic regression model using the lasso. Let's try it out!

```{r}
plr_mod <- 
  logistic_reg(penalty = .01, mixture = 1) %>% 
  set_engine("glmnet") %>% 
  set_mode("classification")

plr_mod %>% 
  translate()
```


Answer:
```{r}
glmnet_wf <-
  knn_wf %>% 
  update_model(plr_mod)

glmnet_wf %>% 
  fit_resamples(resamples = alz_folds) %>% 
  collect_metrics()
```


